CF-SuGAR Power Calculations

### 2025-03-28 Christine Chan/CF-SuGAR/power_calculations.qmd
CF-SuGAR power calculations plus FEV1
more CF-SuGAR power stuff

```{r}
registry$bmi[registry$bmi >= 200] <- NA
# A1c group
registry$a1c_group <- cut(registry$A_hgba1c, c(-Inf, 5.9, Inf))
registry$a1c_group <- relevel(registry$a1c_group, ref = "(5.9, Inf]")
# Remove people with CFRD
registry <- registry %>%
  filter(CFRD != "CFRD+") %>%
  arrange(eDWID, ReviewYear)
# Write for SAS
write.csv(registry,
  file = "./CF-SuGAR/Background/Power Calculations/Data/registry.csv",
  row.names = F, na = ""
)
# Proportion of good and bad A1c
# Overall
prop.table(table(registry$a1c_group))
# By person (take each person's worst)
t <- registry %>%
  group_by(eDWID) %>%
  summarise(
    a1c_group = ifelse(any(a1c_group == "(5.9, Inf]"), "(5.9, Inf]", "(-Inf,5.9]")
  )
prop.table(table(t$a1c_group))
```

@@

```{r}
mod1 <- lmer(bmi ~ a1c_group + Age_YrEnd + (Age_YrEnd | eDWID),
  data = registry
)
summary(mod1, ddf = "Kenward-Roger")
```

@@

>>>>

```{r}
registry$bmi[registry$bmi >= 200] <- NA
# A1c group
registry$a1c_group <- as.numeric(registry$A_hgba1c <= 5.9)
# Remove people with CFRD
registry <- registry %>%
  filter(CFRD != "CFRD+") %>%
  arrange(eDWID, ReviewYear)
# Write for SAS
write.csv(registry,
  file = "./CF-SuGAR/Background/Power Calculations/Data/registry.csv",
  row.names = F, na = ""
)
# Proportion of good and bad A1c
# Overall
prop.table(table(registry$a1c_group))
# By person (take each person's worst)
t <- registry %>%
  group_by(eDWID) %>%
  summarise(
    a1c_group = ifelse(any(a1c_group == "(5.9, Inf]"), "(5.9, Inf]", "(-Inf,5.9]")
  )
prop.table(table(t$a1c_group))
```

@@

```{r}
bmi_mod <- lm(BMI ~ age + as.numeric(Baseline_1hr_glucose >= 140), data = lorenz)
summary(bmi_mod)
sd(resid(bmi_mod))
prop.table(table(lorenz$Baseline_1hr_glucose >= 140))
```

@@

```{r}
fev1_mod <- lm(FEV1.per.pred ~ age + as.numeric(Baseline_1hr_glucose >= 140), data = lorenz)
summary(fev1_mod)
sd(resid(fev1_mod))
```
